A Survey of Current Exoskeletons\\ and Their Control Architectures and Algorithms\\ (Draft 3.2)

### 2015-09-30 control.tex
more updates

>>>>

\subsection{Bias}

If you ask people who research complex computationally expensive
high end control
systems for a living how to control a system,
they will recommend complex computationally expensive high end control systems.
It is entirely possible that simple local low dimensional controllers
designed using traditional (frequency domain) techniques will do
quite well, especially if the appropriate sensors (such as 
operator-exoskeleton force sensors) are available.

### 2015-09-30 survey.tex
more updates

\title{A Survey of Current Exoskeletons and Their Control Architectures and
Algorithms\\
(Draft 3.1)}

@@

We then list other systems in a variety of categories.

@@

>>>>

\title{A Survey of Current Exoskeletons\\ and Their Control Architectures and
Algorithms\\
(Draft 3.2)}

@@

We then list other exoskeletons in a variety of categories.

@@

\newpage
